Type cones of $\b{g}$-vector fans

### 2019-02-05 thirdPaper/draft/typeConeAssociahedra.tex
draft introduction cluster algebras

% math special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\HH}{\mathbb{H}} % hyperplane
\newcommand{\K}{k} % field
\newcommand{\fA}{\mathfrak{A}} % alternating group
\newcommand{\fS}{\mathfrak{S}} % symmetric group
\newcommand{\cA}{\mathcal{A}} % algebra
\newcommand{\cC}{\mathcal{C}} % collection
\newcommand{\cS}{\mathcal{S}} % ground set
\newcommand{\uR}{\underline{R}} % underline set
\newcommand{\uS}{\underline{S}} % underline set
\newcommand{\uT}{\underline{T}} % underline set
\newcommand{\oS}{\overline{S}} % overline set
\newcommand{\ucS}{\underline{\cS}} % underline ground set
\renewcommand{\b}[1]{{\boldsymbol{#1}}} % bold letters
\newcommand{\h}{\widehat} % hat letters

% math commands
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % big set notation
\newcommand{\Bigset}[2]{\Big\{ #1 \;\Big|\; #2 \Big\}} % Big set notation
\newcommand{\setangle}[2]{\left\langle #1 \;\middle|\; #2 \right\rangle} % set notation
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\dotprod}[2]{\left\langle \, #1 \; \middle| \; #2 \, \right\rangle} % dot product
\newcommand{\symdif}{\,\triangle\,} % symmetric difference
\newcommand{\one}{{1\!\!1}} % the all one vector
\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\simplex}{\triangle} % simplex
\renewcommand{\implies}{\Rightarrow} % imply sign
\newcommand{\transpose}[1]{{#1}^t} % transpose matrix

@@

% geometry
\newcommandx{\Asso}[2][1=n,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
\newcommandx{\Zono}[2][1=n,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
\newcommand{\Fan}{\mathcal{F}} % fan
\newcommand{\multiplicityVector}{\b{m}} % multiplicity vector
\newcommandx{\ray}[1][1=r]{\b{#1}} % ray
\newcommandx{\rays}[1][1=R]{\b{#1}} % rays
\newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of the path #1
\newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of the paths #1
\newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}(#1)} % g-vector fan

@@

@@

@@

@@

\begin{proposition}
\label{prop:exchangeablePairsAsso}
%Consider two exchangeable proper intervals~$[i,j]$ and~$[\ell,k]$ of~$[n+1]$, corresponding to two crossing diagonals~$(i-1,j+1)$ and~$(k-1,\ell+1)$ of the $(n+3)$-gon with~$0 \le i-1 < k-1 < j+1 < \ell+1 \le n+2$.
Consider two crossing diagonals~$(a,b)$ and~$(a',b')$, and any two triangulations~$T, T'$ such that~$T \ssm \{(a,b)\} = T' \ssm \{(a',b')\}$.
Then both triangulations~$T$ and~$T'$ contain the square $aa'bb'$, and the linear dependence between the $\b{g}$-vectors of~$T \cup T'$ is given by
\[
\gvector{a,b} + \gvector{a',b'} = \gvector{a,b'} + \gvector{a',b}.
\]
In particular, the fan~$\gvectorFan[n]$ has the unique exchange property.
\end{proposition}

@@

The acyclic and simply-laced case was treated in~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
Computer experiments indicate that the type cone is always simplicial for any seed (acyclic or not) in any finite type cluster algebra.
While the case of acyclic seeds can be handled by representation theory~\cite{BazierMatteDouvilleMousavandThomasYildirim}, we have no proof at the moment for cyclic seeds.

@@

\para{Non-kissing fan and gentle associahedron}
%
Let~$(\b{e}_v)_{v \in Q_0}$ denote the canonical basis of~$\R^{Q_0}$.
For a multiset~$V = \{\!\{v_1, \dots, v_k\}\!\}$ of~$Q_0$, we denote by $\multiplicityVector_V \eqdef \sum_{i \in [k]} \b{e}_{v_i}$.
The \defn{$\b{g}$-vector} of a walk~$\omega$ is the vector~$\gvector{\omega} \in \R^{Q_0}$ defined by~$\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}$.
Note that by definition, the $\gvector{\omega} = 0$ for a straight walk~$\omega$.
We also define~$\gvectors{F} \eqdef \set{\gvector{\omega}}{\omega \in F}$ for a face~$F$ of~$\NKC$.
These vectors support a complete simplicial fan realization of the non-kissing complex complex.
Examples are illustrated in \cref{fig:nonkissingFans}.

@@

\begin{theorem}[{\cite[Thm.~4.27]{PaluPilaudPlamondon-nonkissing}}]
For any non-kissing finite gentle quiver~$\quiver$, the non-kissing fan~$\gvectorFan[\quiver]$ is the normal fan of the gentle associahedron~$\Asso[\quiver]$, defined as the intersection of the half-spaces~$\set{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$ for all walks~$\omega \in \properWalks$.
\end{theorem}

@@

\begin{proposition}
For any gentle quiver~$\quiver$ with no self-kissing walk and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
\end{proposition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relations for~$\b{g}$-vectors in~$2$-Calabi--Yau triangulated categories}
%%%%%
\subsection{Setting}\label{sect::setting}
Let~$\field$ be a field.  Let~$\cat$ be a~$\field$-linear triangulated category with suspension functor~$\susp$.  We fix a collection~$\ind(\cat)$ of representatives of isomorphism classes of indecomposable objects of~$\cat$. We will assume the following:
\begin{itemize}
 \item $\cat$ is essentially small (in particular,~$\ind(\cat)$ is a set);
 \item $\cat$ is~$\Hom{}$-finite: for each pair of objects~$X$ and~$Y$, the~$\field$-vector space~$\cat(X,Y)$ is finite-dimensional;
 \item $\cat$ is Krull--Schmidt: the endomorphism algebra of any indecomposable object is local;
 \item $\cat$ is~$2$-Calabi--Yau: for each pair of objects~$X$ and~$Y$, there is an isomorphism of bifunctors
 \[
  \cat(X,\susp Y) \to D\cat(Y,\susp X)
 \]
 where~$D=\Hom{\field}(-,\field)$ is the usual duality of vector spaces;
 \item $\cat$ contains a basic cluster-tilting object~$T=\bigoplus_{i=1}^n T_i$:
 \[
  \textrm{for any object~$X$,} \quad \cat(T, \susp X) = 0 \quad \textrm{if and only if} \quad X\in \add(T),
 \]
 where~$\add(T)$ is the smallest additive full subcategory of~$\cat$ containing the~$T_i$'s and closed under isomorphisms.
\end{itemize}

%%%%
\subsection{Statement of the theorem}
We need to introduce some notations before stating the main result of this section.  Let~$\Lambda:= \End{\cat}(T)$, and let~$F$ be the functor
\[
 F=\cat(T,-):\cat \xrightarrow{} \MOD \Lambda.
\]
\begin{proposition}[\cite{BuanMarshReiten, KellerReiten}]
 The functor~$F$ induces an equivalence of~$\field$-linear categories
 \[
  F:\cat/(\susp T) \xrightarrow{} \MOD \Lambda,
 \]
 where~$(\susp T)$ is the ideal of morphisms factoring through an object of~$\add(\susp T)$ and~$\MOD \Lambda$ is the category of finite-dimensional right~$\Lambda$-modules.  This equivalence induces further equivalences between~$\add(T)$ and the category of projective modules, and between~$\add(\susp^2 T)$ and that of injective modules.
\end{proposition}

@@

%%%%
\subsection{Proof of Theorem \ref{theo::relations-g-vecteurs}}

@@

%%%%
\subsection{Application to~$\b g$-vectors}\label{sect::applications-g-vectors}

>>>>

% math special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\Q}{\mathbb{Q}} % rationals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\HH}{\mathbb{H}} % hyperplane
\newcommand{\K}{k} % field
\newcommand{\fA}{\mathfrak{A}} % alternating group
\newcommand{\fS}{\mathfrak{S}} % symmetric group
\newcommand{\cA}{\mathcal{A}} % algebra
\newcommand{\cC}{\mathcal{C}} % collection
\newcommand{\cS}{\mathcal{S}} % ground set
\newcommand{\uR}{\underline{R}} % underline set
\newcommand{\uS}{\underline{S}} % underline set
\newcommand{\uT}{\underline{T}} % underline set
\newcommand{\oS}{\overline{S}} % overline set
\newcommand{\ucS}{\underline{\cS}} % underline ground set
\renewcommand{\b}[1]{{\boldsymbol{#1}}} % bold letters
\newcommand{\h}{\widehat} % hat letters

% math commands
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % big set notation
\newcommand{\Bigset}[2]{\Big\{ #1 \;\Big|\; #2 \Big\}} % Big set notation
\newcommand{\setangle}[2]{\left\langle #1 \;\middle|\; #2 \right\rangle} % set notation
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\dotprod}[2]{\left\langle \, #1 \; \middle| \; #2 \, \right\rangle} % dot product
\newcommand{\bigdotprod}[2]{\big\langle \, #1 \; \big| \; #2 \, \big\rangle} % dot product
\newcommand{\symdif}{\,\triangle\,} % symmetric difference
\newcommand{\one}{{1\!\!1}} % the all one vector
\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\simplex}{\triangle} % simplex
\renewcommand{\implies}{\Rightarrow} % imply sign
\newcommand{\transpose}[1]{{#1}^T} % transpose matrix

@@

% geometry
\newcommandx{\Asso}[2][1=n,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
\newcommandx{\Zono}[2][1=n,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
\newcommand{\Fan}{\mathcal{F}} % fan
\newcommand{\multiplicityVector}{\b{m}} % multiplicity vector
\newcommandx{\ray}[1][1=r]{\b{#1}} % ray
\newcommandx{\rays}[1][1=R]{\b{#1}} % rays
\newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of the path #1
\newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of the paths #1
\newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}(#1)} % g-vector fan
\newcommand{\cvector}[3]{\mathbf{c}(#1, #3 \in #2)} % c-vector of the cluster variable #3 in the cluster #2 with respect to the initial cluster #1
\newcommand{\cvectors}[2]{\mathbf{c}(#1, #2)} % c-vectors of the cluster #2 with respect to the initial cluster #1

@@

% Cluster algebras
\newcommand{\Trop}[1]{\mathbb{P}_{#1}} % tropical semifield
\newcommand{\positiveExponents}[1]{\left\{#1\right\}_+} % positive exponents in tropical semifield
\newcommand{\negativeExponents}[1]{\left\{#1\right\}_-} % negative exponents in tropical semifield
\newcommand{\seed}{\Sigma} % a cluster
\newcommand{\cluster}{\mathrm{X}} % a cluster
\newcommandx{\clusters}{\mathcal{X}} % all clusters
\newcommand{\coefficients}{\mathrm{P}} % a coefficients tuple
\newcommandx{\clusterAlgebra}[2][1=\B_\circ, 2=\coefficients_\circ]{\mathcal{A}\!\left(#1,#2\right)} % cluster algebra
\newcommandx{\principalClusterAlgebra}[1][1=\B_\circ]{\mathcal{A}_{\mathrm{pr}}\left(#1\right)} % principal coefficients cluster algebra
\newcommandx{\coefficientFreeClusterAlgebra}[1][1=\B_\circ]{\mathcal{A}_{\mathrm{fr}}(#1)} % coefficient free cluster algebra
\newcommandx{\clusterComplex}[1][1=\B_\circ]{\Delta(#1)} % cluster complex
\newcommand{\B}{\mathrm{B}} % b-matrix
\newcommand{\A}[1]{\mathrm{A}({#1})} % b-matrix
\newcommand{\D}{\mathrm{D}} % symmetrizer
\newcommand{\simpleRoot}{\alpha} % simple root
\newcommand{\fundamentalWeight}{\omega} % fundamental weights

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%

@@

\begin{proposition}
\label{prop:exchangeablePairsAsso}
%Consider two exchangeable proper intervals~$[i,j]$ and~$[\ell,k]$ of~$[n+1]$, corresponding to two crossing diagonals~$(i-1,j+1)$ and~$(k-1,\ell+1)$ of the $(n+3)$-gon with~$0 \le i-1 < k-1 < j+1 < \ell+1 \le n+2$.
Let~$(a,b)$ and~$(a',b')$ be two crossing diagonals with~${0 \le a < a' < b < b' \le n+2}$, and let~$T$ and~$T'$ be any two triangulations such that~$T \ssm \{(a,b)\} = T' \ssm \{(a',b')\}$.
Then both triangulations~$T$ and~$T'$ contain the square $aa'bb'$, and the linear dependence between the $\b{g}$-vectors of~$T \cup T'$ is given by
\[
\gvector{a,b} + \gvector{a',b'} = \gvector{a,b'} + \gvector{a',b}.
\]
In particular, the fan~$\gvectorFan[n]$ has the unique exchange property.
\end{proposition}

@@

We now extend the results of the previous section to the $\b{g}$-vector fan of any finite type cluster algebra with respect to any seed (acyclic or not).
Cluster algebras were introduced by S.~Fomin and A.~Zelevinsky~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
Here, we will focus on finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasII} and more specifically on properties of their $\b{g}$-vectors~\cite{FominZelevinsky-ClusterAlgebrasIV}.
These $\b{g}$-vectors support a complete simplicial fan, which is known to be the normal fan of a polytope called generalized associahedron. These polytopal realizations were first constructed for bipartite initial seeds by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} using the $\b{d}$-vector fans of~\cite{FominZelevinsky-YSystems}, then for acyclic initial seeds by C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} using Cambrian lattices and fans of N.~Reading and D.~Speyer~\cite{Reading-CambrianLattices, ReadingSpeyer}, and revisited by S.~Stella~\cite{Stella}, and by V.~Pilaud and C.~Stump~\cite{PilaudStump-brickPolytope} via brick polytopes, and finally for arbitrary initial seeds by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella}.

\para{Cluster algebras}
%
Let~$\Q(x_1, \dots, x_n, p_1, \dots, p_m)$ be the field of rational expressions in~$n+m$ variables with rational coefficients, and~$\Trop{m}$ denote its abelian multiplicative subgroup generated by~$\{p_i\}_{i \in [m]}$.
For~$p = \prod\limits_{i \in [m]} p_i^{a_i} \in \Trop{m}$, define
\(
\positiveExponents{p} \eqdef \prod\limits_{i \in [m]} p_i^{\max(a_i,0)}
\)
and
\(
\negativeExponents{p} \eqdef \prod\limits_{i \in [m]} p_i^{-\min(a_i,0)}
\).
%so that~$p = \positiveExponents{p} \negativeExponents{p}^{-1}$.

\medskip
A \defn{seed}~$\seed$ is a triple~$(\B, \coefficients, \cluster)$ where
\begin{itemize}
\item the \defn{exchange matrix}~$\B$ is an integer~$n \times n$ skew-symmetrizable matrix, \ie such that there exists a diagonal matrix~$\D$ with~$-\B\D = (\B\D)^T$,
\item the \defn{coefficient tuple}~$\coefficients$ is any subset of~$n$ elements of~$\Trop{m}$,
\item the \defn{cluster}~$\cluster$ is a set of~$n$ \defn{cluster variables} in~$\Q(x_1, \dots, x_n, p_1, \dots, p_m)$ algebraically independent over~$\Q(p_1, \dots, p_m)$.
\end{itemize}
To simplify our notations, we use the convention to label~$\B = (b_{xy})_{x,y \in \cluster}$ and~$\coefficients = \{p_x\}_{x \in \cluster}$ by the cluster variables of~$\cluster$.

For a seed~$\seed = (\B, \coefficients, \cluster)$ and a cluster variable~$x \in \seed$, the \defn{mutation} in direction~$x$ creates a new seed~$\mu_x(\seed) = \seed' = (\B', \coefficients', \cluster')$ where:
\begin{itemize}
\item the new cluster $\cluster'$ is obtained from $\cluster$ by replacing $x$ with the cluster variable $x'$ defined by the following \defn{exchange relation}:
\[
x x' = \positiveExponents{p_x} \prod_{{y \in \cluster, \; b_{xy}  > 0}} y^{b_{xy}} + \negativeExponents{p_x} \prod_{{y \in \cluster, \; b_{xy}  <0}} y^{-b_{xy}}
\]
and leaving the remaining cluster variables unchanged so that $\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$.

\item the row (resp.~column) of~$\B'$ indexed by~$x'$ is the negative of the row (resp.~column) of~$\B$ indexed by~$x$, while all other entries satisfy
\(
b'_{yz} = b_{yz} + \frac{1}{2}\big(|b_{yx}| b_{xz} + b_{yx}|b_{xz}|\big),
\)

\item the elements of the new coefficient tuple $\coefficients'$ are 
\[
p'_y =
\begin{cases}
	p_x^{-1}  & \text{if } y = x', \\
	p_y\negativeExponents{p_x}^{b_{xy}}  & \text{if } y \neq x' \text{ and } b_{xy} \leq 0, \\
	p_y\positiveExponents{p_x}^{b_{xy}}  & \text{if } y \neq x' \text{ and } b_{xy} > 0,
\end{cases}
\]
\end{itemize}
An important point is that mutations are involutions: $\mu_{x'} \big( \mu_{x}(\seed) \big) = \seed$.
We say that two seeds are \defn{mutationally equivalent} when they can be obtained from each other by a sequence of mutations (we also use the same terminology for exchange matrices).
%We consider an \defn{initial seed} $\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ whose cluster variables are supposed to be~$x_1, \dots, x_n$.

\begin{definition}[{\cite[Definition~2.11]{FominZelevinsky-ClusterAlgebrasIV}}]
The (geometric type) \defn{cluster algebra} $\clusterAlgebra$ is the $\Z\Trop{m}$-subring of~$\Q(x_1, \dots, x_n, p_1, \dots, p_m)$ generated by all the cluster variables in all the seeds mutationally equivalent to an initial seed~$\seed_\circ = (\B_\circ, \coefficients_\circ, \cluster_\circ)$ with cluster variables~$\cluster_\circ = \{x_1, \dots, x_n\}$.
\end{definition}

The \defn{cluster complex} of~$\clusterAlgebra$ is the simplicial complex whose vertices are the cluster variables of~$\clusterAlgebra$ and whose facets are the clusters of~$\clusterAlgebra$.

\para{Finite type}
%
In this paper, we only consider \defn{finite type} cluster algebras, \ie those having only finitely many cluster variables.
It turns out that these finite type cluster algebras were classified by S.~Fomin and A.~Zelevinsky~\cite{FominZelevinsky-ClusterAlgebrasII} using the Cartan-killing classification for crystallographic root systems.
Define the \defn{Cartan companion} of an exchange matrix $\B$ as the matrix~$\A{\B}$ given by~$a_{xy} = 2$ if~$x = y$ and~$a_{xy} = -|b_{xy}|$ otherwise.

\begin{theorem}[{\cite[Theorem~1.4]{FominZelevinsky-ClusterAlgebrasII}}]
\label{thm:finiteTypeClassification}
The cluster algebra~$\clusterAlgebra$ is of finite type if and only~if $\B_\circ$ is mutationally equivalent to a matrix~$\B$ whose Cartan companion~$\A{\B}$ is a Cartan matrix of finite type. Moreover the type of $\A{\B}$ is determined~by~$B_\circ$.
\end{theorem}

A finite type exchange matrix~$\B_\circ$ is \defn{acyclic} if~$\A{\B_\circ}$ is already a Cartan matrix, and \defn{cyclic} otherwise.
An acyclic exchange matrix~$\B_\circ$ is \defn{bipartite} if each row of~$\B_\circ$ consists either of non-positive or non-negative entries.
We use the same terminology for the seed~$\seed_\circ$.

From now on, we fix a finite type cluster algebra~$\clusterAlgebra$ and we consider the root system of type~$\A{\B_\circ}$ (again, this root system is finite only when the initial seed~$\B_\circ$ is acyclic). We use the following classical bases of the underlying vector spaces:
\begin{itemize}
\item the simple roots~$\{\simpleRoot_x\}_{x \in \cluster_\circ}$ and the fundamental weights~$\{\fundamentalWeight_x\}_{x \in \cluster_\circ}$ are two bases of the same vector space~$V$ related by the Cartan matrix~$\A{\B_\circ}$,
\item the simple coroots~$\{\simpleRoot^\vee_x\}_{x \in \cluster_\circ}$ and the fundamental coweights~$\{\fundamentalWeight^\vee_x\}_{x \in \cluster_\circ}$ are two basis of the dual space~$V^\vee$ related by the transpose of the Cartan matrix~$\transpose{\A{\B_\circ}}$,
\end{itemize}
and the basis of simple roots is dual to the basis of fundamental coweights, while the basis of fundamental weights is dual to the basis of simple coroots.

The cluster complex of a finite cluster algebra~$\clusterAlgebra$ is independent of the choice of coefficients and of the choice of the initial seed (as long at it remains in the same mutation class), and therefore only depends on the cluster type of~$\clusterAlgebra$ (\ie the Cartan type of~$\A(\B)$ in \cref{thm:finiteTypeClassification}).
Moreover, for~$\B_\circ^\vee \eqdef -\transpose{\B_\circ}$, then the map sending a cluster variable~$x$ in a seed~$\seed$ of~$\clusterAlgebra$ to the cluster variable~$x^\vee$ in the seed~$\seed^\vee$ of~$\principalClusterAlgebra[\B_\circ^\vee]$ obtained by the same sequence of mutations defines a natural isomorphism between the cluster complexes of~$\clusterAlgebra$ and~$\clusterAlgebra[\B_\circ^\vee]$.

\para{Principal coefficients and $\b{g}$- and $\b{c}$-vectors}
%
We now consider principal coefficients to define the $\b{g}$- and $\b{c}$-vectors.

\begin{definition}[{\cite[Definition~3.1]{FominZelevinsky-ClusterAlgebrasIV}}]
The cluster algebra with \defn{principal coefficients} at~$\B_\circ$ is the cluster algebra~$\principalClusterAlgebra \eqdef \clusterAlgebra[\B_\circ][\coefficients_\circ]$ in~$\Q(x_1, \dots, x_n, p_1, \dots, p_n)$, where~$\coefficients_\circ = \{p_x\}_{x \in \cluster_\circ}$ are precisely the generators~$p_1, \dots, p_n$ of~$\Trop{n}$ relabeled by~$\cluster_\circ$.
\end{definition}

Cluster algebras with principal coefficients are $\Z^n$-graded (in the basis~$\{\omega_x\}_{x \in \cluster_\circ}$ of~$V$).
The degree function~$\deg(\B_\circ,\cdot)$ on $\principalClusterAlgebra$ is obtained by setting
\(
\deg(\B_\circ,  x) \eqdef \fundamentalWeight_x
\)
and
\(
\deg(\B_\circ, p_x) \eqdef \sum_{y \in \cluster_\circ} -b_{yx} \fundamentalWeight_y
\)
for any $x\in\cluster_\circ$.
This assignment makes all exchange relations and all cluster variables in~$\principalClusterAlgebra$ homogeneous~\cite{FominZelevinsky-ClusterAlgebrasIV} and it justifies the definition of the following family of integer vectors associated to cluster variables.

\begin{definition}[\cite{FominZelevinsky-ClusterAlgebrasIV}]
The \defn{$\b{g}$-vector}~$\gvector{\B_\circ}{x}$ of a cluster variable~$x \in \principalClusterAlgebra$ is its degree.
We denote by $\gvectors{\B_\circ}{\seed} \eqdef \set{\gvector{\B_\circ}{x}}{x \in \seed}$ the set of $\b{g}$-vectors of the cluster variable in the seed~$\seed$ of~$\principalClusterAlgebra$.
\end{definition}

The next definition gives another family of integer vectors, introduced implicitly in~\cite{FominZelevinsky-ClusterAlgebrasIV}, that are relevant in the structure of~$\principalClusterAlgebra$.

\begin{definition}
Given a seed~$\seed$ in~$\principalClusterAlgebra$, the \defn{$\b{c}$-vector} of a cluster variable $x \in \seed$ is the vector
\(
\cvector{\B_\circ}{\seed}{x} \eqdef \sum_{y \in \cluster_\circ} c_{yx} \, \simpleRoot_y
\)
of exponents of~$p_x = \prod_{y \in \cluster_\circ} (p_y)^{c_{yx}}$.
We denote by~$\cvectors{\B_\circ}{\seed} \eqdef \set{\cvector{\B_\circ}{\seed}{x}}{x \in \seed}$ the set of $\b{c}$-vectors of a seed~$\seed$.
\end{definition}

These two families of vectors are connected via the isomorphism~$x \mapsto x^\vee$ between the cluster complexes of~$\principalClusterAlgebra$ and~$\principalClusterAlgebra[\B_\circ^\vee]$ described above.

\begin{theorem}[{\cite[Theorem~1.2]{NakanishiZelevinsky}}]
\label{thm:duality}
For any seed~$\seed$ of~$\principalClusterAlgebra$, let $\seed^\vee$ be its dual in $\principalClusterAlgebra[\B_\circ^\vee]$.
Then the set of $\b{g}$-vectors~$\gvector{\B_\circ}{\seed}$ and the set of $\b{c}$-vectors~$\cvectors{\B_\circ^\vee}{\seed^\vee}$ form dual bases, that is
\(
{\bigdotprod{\gvector{\B_\circ}{x}}{\cvector{\B_\circ^\vee}{\seed^\vee}{y^\vee}} = \delta_{x=y}}
\)
for any two cluster variables~$x,y \in \seed$.
\end{theorem}

\para{The $\b{g}$-vector fan}
%
The following statement is well known.
\vincent{Explain}

\begin{theorem}
\label{thm:gvectorFan}
For any finite type exchange matrix~$\B_\circ$, the collection of cones \\[.1cm]
\centerline{
$\gvectorFan[\B_\circ] \eqdef \bigset{\R_{\ge0} \gvectors{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},$
} \\[.1cm]
together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} of~$\B_\circ$.
\end{theorem}

Moreover, this fan is known to be polytopal.

\begin{theorem}[{\cite[Thm.~26]{HohlwegPilaudStella}}]
\label{thm:gvectorFan}
For any finite type exchange matrix~$\B_\circ$, the $\b{g}$-vector fan~$\gvectorFan[\B_\circ]$ is the normal fan of the polytope defined by...
\vincent{TODO}
\end{theorem}

\para{Flips in the $\b{g}$-vector fan}

\newpage
The acyclic and simply-laced case was treated in~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
Computer experiments indicate that the type cone is always simplicial for any seed (acyclic or not) in any finite type cluster algebra.
While the case of acyclic seeds can be handled by representation theory~\cite{BazierMatteDouvilleMousavandThomasYildirim}, we have no proof at the moment for cyclic seeds.

@@

\para{Non-kissing fan and gentle associahedron}
%
Let~$(\b{e}_v)_{v \in Q_0}$ denote the canonical basis of~$\R^{Q_0}$.
For a multiset~$V = \{\!\{v_1, \dots, v_k\}\!\}$ of~$Q_0$, we denote by $\multiplicityVector_V \eqdef \sum_{i \in [k]} \b{e}_{v_i}$.
The \defn{$\b{g}$-vector} of a walk~$\omega$ is the vector~$\gvector{\omega} \in \R^{Q_0}$ defined by~$\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}$.
Note that by definition, the $\gvector{\omega} = 0$ for a straight walk~$\omega$.
We also define~$\gvectors{F} \eqdef \set{\gvector{\omega}}{\omega \in F}$ for a face~$F$ of~$\NKC$.
These vectors support a complete simplicial fan realization of the non-kissing complex complex.
Examples are illustrated in \cref{fig:nonkissingFans}.
\vincent{Define $\b{c}$-vectors}

@@

\begin{theorem}[{\cite[Thm.~4.27]{PaluPilaudPlamondon-nonkissing}}]
For any non-kissing finite gentle quiver~$\quiver$, the non-kissing fan~$\gvectorFan[\quiver]$ is the normal fan of the gentle associahedron~$\Asso[\quiver]$, defined as the intersection of the half-spaces~$\set{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$ for all walks~$\omega \in \properWalks$.
\vincent{Give the vertex description using $c$-vectors}
\end{theorem}

@@

\begin{proposition}
For any gentle quiver~$\quiver$ with no self-kissing walk and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
\vincent{This is FALSE...}
\end{proposition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Relations for~$\b{g}$-vectors in~$2$-Calabi--Yau triangulated categories}

%%%%%%%%%%%

\subsection{Setting}\label{sect::setting}
Let~$\field$ be a field.  Let~$\cat$ be a~$\field$-linear triangulated category with suspension functor~$\susp$.  We fix a collection~$\ind(\cat)$ of representatives of isomorphism classes of indecomposable objects of~$\cat$. We will assume the following:
\begin{itemize}
 \item $\cat$ is essentially small (in particular,~$\ind(\cat)$ is a set);
 \item $\cat$ is~$\Hom{}$-finite: for each pair of objects~$X$ and~$Y$, the~$\field$-vector space~$\cat(X,Y)$ is finite-dimensional;
 \item $\cat$ is Krull--Schmidt: the endomorphism algebra of any indecomposable object is local;
 \item $\cat$ is~$2$-Calabi--Yau: for each pair of objects~$X$ and~$Y$, there is an isomorphism of bifunctors
 \[
  \cat(X,\susp Y) \to D\cat(Y,\susp X)
 \]
 where~$D=\Hom{\field}(-,\field)$ is the usual duality of vector spaces;
 \item $\cat$ contains a basic cluster-tilting object~$T=\bigoplus_{i=1}^n T_i$:
 \[
  \textrm{for any object~$X$,} \quad \cat(T, \susp X) = 0 \quad \textrm{if and only if} \quad X\in \add(T),
 \]
 where~$\add(T)$ is the smallest additive full subcategory of~$\cat$ containing the~$T_i$'s and closed under isomorphisms.
\end{itemize}

%%%%%%%%%%%

\subsection{Statement of the theorem}
We need to introduce some notations before stating the main result of this section.  Let~$\Lambda:= \End{\cat}(T)$, and let~$F$ be the functor
\[
 F=\cat(T,-):\cat \xrightarrow{} \MOD \Lambda.
\]
\begin{proposition}[\cite{BuanMarshReiten, KellerReiten}]
 The functor~$F$ induces an equivalence of~$\field$-linear categories
 \[
  F:\cat/(\susp T) \xrightarrow{} \MOD \Lambda,
 \]
 where~$(\susp T)$ is the ideal of morphisms factoring through an object of~$\add(\susp T)$ and~$\MOD \Lambda$ is the category of finite-dimensional right~$\Lambda$-modules.  This equivalence induces further equivalences between~$\add(T)$ and the category of projective modules, and between~$\add(\susp^2 T)$ and that of injective modules.
\end{proposition}

@@

%%%%%%%%%%%

\subsection{Proof of Theorem \ref{theo::relations-g-vecteurs}}

@@

%%%%%%%%%%%

\subsection{Application to~$\b g$-vectors}\label{sect::applications-g-vectors}
